COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-05-04 paper_files/figure-latex/fig3paper-1.tex
drop drive calls
update
no google drive
paper
update files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,547.64) rectangle (371.71,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,547.64) rectangle (371.71,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
	(371.71,560.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
	(371.71,580.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
	(371.71,599.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
	(371.71,619.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,551.28) --
	(371.71,551.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
	(371.71,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
	(371.71,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
	(371.71,609.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,547.64) --
	( 75.24,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,547.64) --
	(120.16,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,547.64) --
	(165.08,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,547.64) --
	(209.99,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,547.64) --
	(254.91,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,547.64) --
	(299.83,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,547.64) --
	(344.75,627.77);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);

\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);

\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);

\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);

\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);

\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);

\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);

\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);

\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);

\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);

\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);

\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);

\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);

\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);

\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);

\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);

\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);

\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);

\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,547.64) rectangle (371.71,627.77);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,462.01) rectangle (371.71,542.14);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,462.01) rectangle (371.71,542.14);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
	(371.71,475.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
	(371.71,494.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
	(371.71,514.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
	(371.71,533.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,465.65) --
	(371.71,465.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
	(371.71,485.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
	(371.71,504.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
	(371.71,523.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,462.01) --
	( 75.24,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,462.01) --
	(120.16,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,462.01) --
	(165.08,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,462.01) --
	(209.99,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,462.01) --
	(254.91,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,462.01) --
	(299.83,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,462.01) --
	(344.75,542.14);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);

\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);

\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);

\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);

\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);

\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);

\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);

\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);

\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);

\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);

\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);

\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);

\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);

\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);

\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);

\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);

\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);

\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,462.01) rectangle (371.71,542.14);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,376.38) rectangle (371.71,456.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,376.38) rectangle (371.71,456.51);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
	(371.71,389.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
	(371.71,409.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
	(371.71,428.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
	(371.71,447.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,380.02) --
	(371.71,380.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
	(371.71,399.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
	(371.71,418.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
	(371.71,438.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,376.38) --
	( 75.24,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,376.38) --
	(120.16,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,376.38) --
	(165.08,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,376.38) --
	(209.99,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,376.38) --
	(254.91,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,376.38) --
	(299.83,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,376.38) --
	(344.75,456.51);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);

\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);

\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);

\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);

\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);

\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);

\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);

\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);

\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);

\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);

\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);

\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);

\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);

\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);

\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);

\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);

\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);

\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,376.38) rectangle (371.71,456.51);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,290.75) rectangle (371.71,370.88);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,290.75) rectangle (371.71,370.88);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
	(371.71,304.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
	(371.71,323.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
	(371.71,342.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
	(371.71,362.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,294.39) --
	(371.71,294.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
	(371.71,313.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
	(371.71,333.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
	(371.71,352.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,290.75) --
	( 75.24,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,290.75) --
	(120.16,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,290.75) --
	(165.08,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,290.75) --
	(209.99,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,290.75) --
	(254.91,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,290.75) --
	(299.83,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,290.75) --
	(344.75,370.88);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);

\path[fill=fillColor] (254.91,294.39) rectangle (275.13,294.39);

\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);

\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);

\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);

\path[fill=fillColor] (234.70,294.39) rectangle (254.91,294.47);

\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);

\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);

\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);

\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);

\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);

\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,290.75) rectangle (371.71,370.88);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,205.12) rectangle (371.71,285.25);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,205.12) rectangle (371.71,285.25);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
	(371.71,218.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
	(371.71,237.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
	(371.71,257.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
	(371.71,276.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,208.76) --
	(371.71,208.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
	(371.71,228.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
	(371.71,247.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
	(371.71,266.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,205.12) --
	( 75.24,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,205.12) --
	(120.16,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,205.12) --
	(165.08,285.25);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:00
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,541.57) rectangle (371.71,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,541.57) rectangle (371.71,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,556.45) --
	(371.71,556.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,578.39) --
	(371.71,578.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,600.33) --
	(371.71,600.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,622.27) --
	(371.71,622.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,545.48) --
	(371.71,545.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,567.42) --
	(371.71,567.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.36) --
	(371.71,589.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,611.30) --
	(371.71,611.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,541.57) --
	( 75.24,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,541.57) --
	(120.16,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,541.57) --
	(165.08,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,541.57) --
	(209.99,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,541.57) --
	(254.91,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,541.57) --
	(299.83,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,541.57) --
	(344.75,627.77);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,545.48) rectangle (185.29,561.63);

\path[fill=fillColor] (234.70,545.48) rectangle (275.13,547.15);

\path[fill=fillColor] (189.78,545.48) rectangle (230.21,547.06);

\path[fill=fillColor] (279.62,545.48) rectangle (320.05,555.66);

\path[fill=fillColor] (324.54,545.48) rectangle (364.97,546.98);

\path[fill=fillColor] ( 55.02,545.48) rectangle ( 95.45,590.77);

\path[fill=fillColor] ( 99.94,545.48) rectangle (140.37,556.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,541.57) rectangle (371.71,627.77);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,449.86) rectangle (371.71,536.07);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,449.86) rectangle (371.71,536.07);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,464.75) --
	(371.71,464.75);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,486.69) --
	(371.71,486.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,508.63) --
	(371.71,508.63);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,530.57) --
	(371.71,530.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,453.78) --
	(371.71,453.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,475.72) --
	(371.71,475.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,497.66) --
	(371.71,497.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,519.60) --
	(371.71,519.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,449.86) --
	( 75.24,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,449.86) --
	(120.16,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,449.86) --
	(165.08,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,449.86) --
	(209.99,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,449.86) --
	(254.91,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,449.86) --
	(299.83,536.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,449.86) --
	(344.75,536.07);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,453.78) rectangle (185.29,485.02);

\path[fill=fillColor] (234.70,453.78) rectangle (275.13,454.13);

\path[fill=fillColor] (189.78,453.78) rectangle (230.21,467.91);

\path[fill=fillColor] (279.62,453.78) rectangle (320.05,454.22);

\path[fill=fillColor] (324.54,453.78) rectangle (364.97,455.88);

\path[fill=fillColor] ( 55.02,453.78) rectangle ( 95.45,492.57);

\path[fill=fillColor] ( 99.94,453.78) rectangle (140.37,454.48);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,449.86) rectangle (371.71,536.07);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,358.15) rectangle (371.71,444.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,358.15) rectangle (371.71,444.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,373.04) --
	(371.71,373.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,394.98) --
	(371.71,394.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,416.92) --
	(371.71,416.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,438.86) --
	(371.71,438.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,362.07) --
	(371.71,362.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,384.01) --
	(371.71,384.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,405.95) --
	(371.71,405.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,427.89) --
	(371.71,427.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,358.15) --
	( 75.24,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,358.15) --
	(120.16,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,358.15) --
	(165.08,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,358.15) --
	(209.99,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,358.15) --
	(254.91,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,358.15) --
	(299.83,444.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,358.15) --
	(344.75,444.36);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,362.07) rectangle (185.29,375.24);

\path[fill=fillColor] (234.70,362.07) rectangle (275.13,362.60);

\path[fill=fillColor] (189.78,362.07) rectangle (230.21,363.04);

\path[fill=fillColor] (279.62,362.07) rectangle (320.05,391.21);

\path[fill=fillColor] (324.54,362.07) rectangle (364.97,362.42);

\path[fill=fillColor] ( 55.02,362.07) rectangle ( 95.45,382.26);

\path[fill=fillColor] ( 99.94,362.07) rectangle (140.37,385.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,358.15) rectangle (371.71,444.36);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,266.45) rectangle (371.71,352.65);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,266.45) rectangle (371.71,352.65);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,281.33) --
	(371.71,281.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,303.27) --
	(371.71,303.27);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,325.21) --
	(371.71,325.21);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,347.15) --
	(371.71,347.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,270.36) --
	(371.71,270.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,292.30) --
	(371.71,292.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,314.24) --
	(371.71,314.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,336.18) --
	(371.71,336.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,266.45) --
	( 75.24,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,266.45) --
	(120.16,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,266.45) --
	(165.08,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,266.45) --
	(209.99,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,266.45) --
	(254.91,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,266.45) --
	(299.83,352.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,266.45) --
	(344.75,352.65);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,270.36) rectangle (185.29,273.09);

\path[fill=fillColor] (234.70,270.36) rectangle (275.13,270.36);

\path[fill=fillColor] (189.78,270.36) rectangle (230.21,271.86);

\path[fill=fillColor] (279.62,270.36) rectangle (320.05,275.46);

\path[fill=fillColor] ( 55.02,270.36) rectangle ( 95.45,348.73);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,266.45) rectangle (371.71,352.65);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,174.74) rectangle (371.71,260.95);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,174.74) rectangle (371.71,260.95);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,189.63) --
	(371.71,189.63);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,211.57) --
	(371.71,211.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,233.51) --
	(371.71,233.51);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,255.45) --
	(371.71,255.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,178.66) --
	(371.71,178.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,200.60) --
	(371.71,200.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,222.54) --
	(371.71,222.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,244.48) --
	(371.71,244.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,174.74) --
	( 75.24,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,174.74) --
	(120.16,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,174.74) --
	(165.08,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,174.74) --
	(209.99,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,174.74) --
	(254.91,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,174.74) --
	(299.83,260.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,174.74) --
	(344.75,260.95);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86,178.66) rectangle (185.29,193.40);

\path[fill=fillColor] (234.70,178.66) rectangle (275.13,179.97);

\path[fill=fillColor] (189.78,178.66) rectangle (230.21,183.31);

\path[fill=fillColor] (279.62,178.66) rectangle (320.05,187.96);

\path[fill=fillColor] (324.54,178.66) rectangle (364.97,180.76);

\path[fill=fillColor] ( 55.02,178.66) rectangle ( 95.45,220.87);

\path[fill=fillColor] ( 99.94,178.66) rectangle (140.37,195.60);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,174.74) rectangle (371.71,260.95);
\end{scope}
\begin{scope}
\path[clip] ( 48.28, 83.03) rectangle (371.71,169.24);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28, 83.03) rectangle (371.71,169.24);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28, 97.92) --
	(371.71, 97.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,119.86) --
	(371.71,119.86);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,141.80) --
	(371.71,141.80);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,163.74) --
	(371.71,163.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28, 86.95) --
	(371.71, 86.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,108.89) --
	(371.71,108.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,130.83) --
	(371.71,130.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,152.77) --
	(371.71,152.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24, 83.03) --
	( 75.24,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16, 83.03) --
	(120.16,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08, 83.03) --
	(165.08,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99, 83.03) --
	(209.99,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91, 83.03) --
	(254.91,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83, 83.03) --
	(299.83,169.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75, 83.03) --
	(344.75,169.24);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (144.86, 86.95) rectangle (185.29, 97.04);

\path[fill=fillColor] (189.78, 86.95) rectangle (230.21, 89.06);

\path[fill=fillColor] (279.62, 86.95) rectangle (320.05,106.17);

\path[fill=fillColor] (324.54, 86.95) rectangle (364.97, 87.04);

\path[fill=fillColor] ( 55.02, 86.95) rectangle ( 95.45,117.23);

\path[fill=fillColor] ( 99.94, 86.95) rectangle (140.37,113.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28, 83.03) rectangle (371.71,169.24);
\end{scope}
\begin{scope}
\path[clip] (393.78,541.57) rectangle (717.20,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,541.57) rectangle (717.20,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,556.45) --
	(717.20,556.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,578.39) --
	(717.20,578.39);
